### 2019-03-29 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Presque bon pour corriger selon les modifications suggérées par Emilie.

This Section starts by giving a unified analysis of regret of the two variants of our algorithm, then we give the finite-time regret bounds for the two variants, with the proof of the first one (the second one is proved in Appendix~\ref{proof:6:mainRegretBound}), which both follows the skeleton of the unified analysis.

@@

%-----------------------------------------------------------------------------
\subsection{Results for \GLRklUCB{} using Global Changes}

\begin{assumption}[Enough samples between two global change-points]
    \label{ass:6:LongPeriodsGlobal}
    Define
    \begin{equation}\label{def:6:DelayGlobal}
        d^{(k)} = d^{(k)}(\alpha,\delta) = \left\lceil \frac{4K}{\alpha\left(\Delta^{(k)}\right)^2}\beta(T,\delta) + \frac{K}{\alpha} \right\rceil.
    \end{equation}
    %
    Then \emph{we assume} that for all change $k \in \{1,\dots,\Upsilon_T\}$,
    $\tau^{(k)} - \tau^{(k-1)} \geq 2\max (d^{(k)},d^{(k-1)})$.
\end{assumption}

@@

\subsection{Results for \GLRklUCB{} using Local Changes}

\begin{assumption}[Enough samples between two local change-points]
    \label{ass:6:LongPeriods}
    Define
    \begin{equation}\label{def:6:DelayLocal}
        d_i^{(\ell)} = d_i^{(\ell)}(\alpha,\delta) = \lceil \frac{4K}{\alpha\left(\Delta_i^{(\ell)}\right)^2}\beta(T,\delta) + \frac{K}{\alpha}\rceil.
    \end{equation}
    %
    Then \emph{we assume} that for all arm $i$ and all change-point of that arm $\ell \in \{1,\dots,\NCi\}$, $\tau_i^{(\ell)} - \tau_i^{(\ell-1)} \geq 2\max (d_i^{(\ell)},d_i^{(\ell-1)})$.
\end{assumption}

% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
\section{Experimental Results}
\label{sec:6:NumericalExperiments}
% ----------------------------------------------------------------------------

@@

We report results obtained on five different piece-wise stationary bandit problems, illustrated in Figures~\ref{fig:6:Problem_1} and \ref{fig:6:Problem_2} above, and Figures~\ref{fig:6:Problem_5}, \ref{fig:6:Problem_4} and \ref{fig:6:Problem_6} below, and described in more details below.
Results are reported with regret tables and regret plots.
For each experiment, the regret was estimated using $1000$ independent runs.

@@

Before giving larger results that compare our approach against other algorithms, we consider the two problems $1$ and $2$ presented above in Figures~\ref{fig:6:Problem_1} and \ref{fig:6:Problem_2} (for $T=5000$).
\emph{For one (random) simulation}, we give below examples of the efficiency of the change-point detection algorithm used by \GLRklUCB{} as well as \CUSUMklUCB{} and \MklUCB,
by giving the times at which they detected a change and reinitialized their memory of observations of one or all the arms.
We also give the number of observations (since the last restart) of the arm on which the change was detected.
As shown below, in the experiments summary, the three change-point detection algorithm give similar performances in terms of regret, but they have different behaviors.
The test in \MUCB{} usually detects less changes, while the test in \CUSUMUCB{} usually detects more changes and even unnecessary changes.
%
On the examples presented below as well as large scale examples, all the tests appear to have no false alarm, and always a small detection delay for changes that are ``easy enough'' to be efficiently detected.
The four algorithms are presented in the order of decreasing performance (\ie, the first one is empirically the most efficient, that is, it obtains a smaller regret in average).

@@

>>>>

This section give the finite-time regret bounds for the two variants, and interpretations of the different results.

% ----------------------------------------------------------------------------
\subsection{Results for \GLRklUCB{} using Global Changes}

\begin{assumption}[Enough samples between two global change-points]
    \label{ass:6:LongPeriodsGlobal}
    Define
    \begin{equation}\label{def:6:DelayGlobal}
        d^{(k)} = d^{(k)}(\alpha,\delta) = \Bigl\lceil \frac{4K}{\alpha\left(\Delta^{(k)}\right)^2}\beta(T,\delta) + \frac{K}{\alpha} \Bigr\rceil.
    \end{equation}
    %
    Then \emph{we assume} that for all change $k \in \{1,\dots,\Upsilon_T\}$,
    $\tau^{(k)} - \tau^{(k-1)} \geq 2\max (d^{(k)},d^{(k-1)})$.
\end{assumption}

% ----------------------------------------------------------------------------
\subsection{Results for \GLRklUCB{} using Local Changes}

\begin{assumption}[Enough samples between two local change-points]
    \label{ass:6:LongPeriods}
    Define
    \begin{equation}\label{def:6:DelayLocal}
        d_i^{(\ell)} = d_i^{(\ell)}(\alpha,\delta) = \Bigl\lceil \frac{4K}{\alpha\left(\Delta_i^{(\ell)}\right)^2}\beta(T,\delta) + \frac{K}{\alpha} \Bigr\rceil.
    \end{equation}
    %
    Then \emph{we assume} that for all arm $i$ and all change-point of that arm $\ell \in \{1,\dots,\NCi\}$, $\tau_i^{(\ell)} - \tau_i^{(\ell-1)} \geq 2\max (d_i^{(\ell)},d_i^{(\ell-1)})$.
\end{assumption}

% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------

%-----------------------------------------------------------------------------
\subsection{Proof of the regret upper-bounds}
\label{sec:6:proofRegret}

\TODOL{Write intro}

This Section starts by giving a unified analysis of regret of the two variants of our algorithm, then we give the proof of the finite-time regret bound for the variant using ``global restarts''.
The proof of the other variant using ``local restarts'' follows the skeleton of the unified analysis, and can be found in Appendix~E of \cite{Besson2019GLRT}.

@@

%-----------------------------------------------------------------------------

@@

\section{Experimental Results}
\label{sec:6:NumericalExperiments}
% ----------------------------------------------------------------------------

@@

We report results obtained on five different piece-wise stationary bandit problems, illustrated in Figures~\ref{fig:6:Problem_1} and \ref{fig:6:Problem_2} above, and Figures~\ref{fig:6:Problem_5}, \ref{fig:6:Problem_4} and \ref{fig:6:Problem_6} below.
% , and described in more details below.
We present regret tables and regret plots,
for which the regret was estimated using $1000$ independent runs.

@@

Before giving larger results that compare our approach against other algorithms, we consider the two problems $1$ and $2$ presented above in Figures~\ref{fig:6:Problem_1} and \ref{fig:6:Problem_2} (for $T=5000$).
\emph{For one (random) simulation}, we give below examples of the efficiency of the change-point detection algorithm used by \GLRklUCB{} as well as \CUSUMklUCB{} and \MklUCB,
by showing the times at which they detect a change and reinitialize their memory of observations of one or all the arms.
We also display the number of observations (since the last restart) of the arm on which the change was detected.
As shown below, in the experiments summary, the three change-point detection algorithm give similar performances in terms of regret, but they have different behaviors.
The test in \MUCB{} usually detects less changes, while the test in \CUSUMUCB{} usually detects more changes and even unnecessary changes.
%
On the examples presented below as well as large scale examples, all the tests appear to have no false alarm, and always a small detection delay for changes that are ``easy enough'' to be efficiently detected.
The four algorithms are presented in the order of decreasing performance (\ie, the first one is empirically the most efficient, that is, it obtains a smaller regret in average).

@@

\TODOL{Conclusion à tirer de cet exemple !}
